Principles for Open Data Curation: A Case Study with the New York City 311 Service Request Data

### 2024-06-14 manuscript/manuscript.tex
Cleanup on line spacing on manuscript.tex

These and other challenges are continually addressed by the various Agency open data managers
as well as the 
\href{https://www.nyc.gov/content/oti/pages/}{NYC Office of Technology and Innovation (OTI)} 
which provides the technology support for the open data system.  
Many of the underlying datasets are updated daily, usually running 1-2 days behind from creation.
However, a number of datasets are updated monthly (such as restaurant inspections), and some are
not updated for one or more years (such as community board boundaries). This poses problems when 
merging dataset with others, as would be expected. Typically, the data must be
exported and manipulated in another, external program. The authors found 
this to be the case with the large 311 dataset employed.

@@

	\item The 10 address-related address fields (incident\_address, 
	street\_name, city, intersection\_street\_1 \& 2, cross\_street\_1 \& 2,  
	landmark, road\_ramp, bridge\_highway\_segment, and 
	taxi\_pick\_up\_location should be in standard USPS format. There 
	are several software packages which can standardize addresses to 
	these standards. We believe such an effort should be automatically 
	applied to these fields at data entry. This step would also greatly 
	improve any underlying geo-coding routines which 	may be used 
	to determine data values such as BBL, latitude, longitude, and New 
	York State X/Y-plane coordinates.

	\item The use of the value ``UNKNOWN'' , ``N/A'', ``NA'', and ``na'' when 
	entered directly as text into a field should be very carefully examined, 
	and in all likelihood prohibited.  There are some indeed a few 
	complaint\_type(s) where an ``N/A'' value is appropriate, such 
	as a consumer\_complaint about certain non-geo centric issues, such 
	as a travel agency or tax preparation service . But even in those cases 
	a value of ``N/A'' should be entered only via a drop-down menu 
	selection. During this analysis, there were far too many data 
	representations of missing data including: <N/A>, ``na'', `` ``, UNKNOWN, 
	and ``N/A''. It's challenging for analyst to have to account for so 
	the many different methods of representing empty or null data fields.

>>>>

These and other challenges are continually addressed by the various Agency open data managers
as well as the 
\href{https://www.nyc.gov/content/oti/pages/}{NYC Office of Technology and Innovation (OTI)} 
which provides the technology support for the open data system.  
Many of the underlying datasets are updated daily, usually running 
1-2 days behind from creation. However, a number of datasets 
are updated monthly (such as restaurant inspections), and some are 
not updated for one or more years (such as community board 
boundaries). This poses problems when merging datasets with 
others, as would be expected. Typically, the data must be exported 
and manipulated in another, external program. The authors found 
this to be the case with the large 311 dataset employed.

@@

	\item The 10 address-related address fields (incident\_address, 
	street\_name, city, intersection\_street\_1 \& 2, cross\_street\_1 \& 2,  
	landmark, road\_ramp, bridge\_highway\_segment, and 
	taxi\_pick\_up\_location should be in standard USPS format. There 
	are several software packages which can standardize addresses to 
	these standards. We believe such an effort should be automatically 
	applied to these fields at data entry. This step would also greatly 
	improve any underlying geocoding routines which 	may be used 
	to determine data values such as BBL, latitude, longitude, and New 
	York State X/Y-plane coordinates.

	\item The use of the value ``UNKNOWN'' , ``N/A'', ``NA'', and ``na'' when 
	entered directly as text into a field should be very carefully examined, 
	and in all likelihood prohibited.  There are some indeed a few 
	complaint\_type(s) where an ``N/A'' value is appropriate, such 
	as a consumer\_complaint about certain non-geocentric issues, such 
	as a travel agency or tax preparation service . But even in those cases 
	a value of ``N/A'' should be entered only via a drop-down menu 
	selection. During this analysis, there were far too many data 
	representations of missing data including: <N/A>, ``na'', `` ``, UNKNOWN, 
	and ``N/A''. It's challenging for analyst to have to account for so 
	the many different methods of representing empty or null data fields.
